Using the internal language of toposes in algebraic geometry

### 2014-06-18 poster.tex
Image credits to Carina
Minor details

\setbeamertemplate{headline}{
 \leavevmode
  \begin{columns}
   \begin{column}{\linewidth}
    \vskip1cm
    \centering
    \usebeamercolor{title in headline}{\color{jblue}\huge{\textbf{\inserttitle}}\\[0.5ex]}
    \usebeamercolor{author in headline}{\color{fg}\large{\insertauthor},}
    \usebeamercolor{institute in headline}{\color{fg}\large{\insertinstitute}\\[1ex]}
    \vskip1cm
   \end{column}
   \vspace{1cm}
  \end{columns}
 %\hspace{0.5in}\begin{beamercolorbox}[wd=\linewidth,colsep=0.15cm]{cboxb}\end{beamercolorbox}
 %\vspace{0.1in}
}

@@

  \begin{block}{What is a topos?}
    A \emph{topos} is a category which has finite limits, is cartesian closed and
    has a subobject classifier. More simply, a topos is a category which has
    similar properties to the category of sets.\medskip

@@

    \includegraphics[width=\columnwidth]{external-internal}
  \end{block}
  \bigskip

@@

    A sheaf is of finite type if and only if, internally, it is a
    finitely generated module. Therefore the proposition follows \emph{at once}
    by interpreting the analogous statement of intuitionistic linear algebra
    in the little Zariski topos:
    Let~$0 \to M' \to M \to M'' \to 0$ be a short exact sequence of modules.
    If~$M'$ and~$M''$ are finitely generated, so is~$M$.\medskip

@@

    This follows \emph{at once} from the following easy proposition of intuitionistic
    linear algebra: Let~$M$ be a finitely generated vector space. Then~$M$ is
    \emph{not not} finite free.
  \end{block}
  \bigskip

@@

    But if~$\F$ is of finite type, the condition can be reformulated using
    generators as ``$x_1 = 0 \wedge \cdots \wedge x_n = 0$''. The meta-theorem
    is applicable to this statement and thus a stalk is zero if and only if~$\F$
    is zero on a neighbourhood.
  \end{block}

  \vspace{1cm}
  \begin{alertblock}{Dictionary of external vs. internal notions}
    Expository notes are available at \url{http://tiny.cc/topos} (work in
    progress).
  \end{alertblock}
  \tiny\rmfamily\justifying
  Tensor product of sheaves $=$ internal ordinary tensor product,
  internal Cartier divisors,
  quasicoherent sheaves $=$ internal ordinary modules satisfying an interesting
  condition,
  more metatheorems about spreading of properties,
  pullback along immersions $=$ internal sheafification,
  relative spectrum $=$ internal spectrum,
  scheme dimension $=$ Krull dimension of~$\O_X$,
  dense $=$ not not,
  further modal operators,
  other toposes,
  group schemes $=$ groups,
  \ldots
\end{column}

@@

* own contributions
* "at once"

>>>>

\setbeamertemplate{headline}{
 \leavevmode
  \begin{columns}
   \begin{column}{\linewidth}
    \vskip1cm
    \centering
    \usebeamercolor{title in headline}{\color{jblue}\huge{\textbf{\inserttitle}}\\[0.5ex]}
    \usebeamercolor{author in headline}{\color{fg}\large{\insertauthor}, }
    \usebeamercolor{institute in headline}{\color{fg}\large{\insertinstitute}\\[1ex]}
    \vskip1cm
   \end{column}
   \vspace{1cm}
  \end{columns}
 %\hspace{0.5in}\begin{beamercolorbox}[wd=\linewidth,colsep=0.15cm]{cboxb}\end{beamercolorbox}
 %\vspace{0.1in}
}

@@

  \begin{block}{What is a topos?}
    A \emph{topos} is a category which has finite limits, is cartesian closed and
    has a subobject classifier. Intuitively, a topos is a category which has
    similar properties to the category of sets.\medskip

@@

    \rotatebox{90}{\tiny Illustration: Carina Willbold}\hspace{-0.25cm}%
    \includegraphics[width=\columnwidth]{external-internal}
  \end{block}
  \bigskip

@@

    A sheaf is of finite type if and only if, internally, it is a
    finitely generated module. Therefore the proposition follows
    \emph{immediately}
    by interpreting the analogous statement of linear algebra
    in the little Zariski topos:
    Let~$0 \to M' \to M \to M'' \to 0$ be a short exact sequence of modules.
    If~$M'$ and~$M''$ are finitely generated, so is~$M$.\medskip

@@

    This is an \emph{immediate} application of the following easy lemma of intuitionistic
    linear algebra: Let~$M$ be a finitely generated vector space. Then~$M$ is
    \emph{not not} finite free.
  \end{block}
  \bigskip

@@

    But if~$\F$ is of finite type, the condition can be reformulated using
    generators as ``$x_1 = 0 \wedge \cdots \wedge x_n = 0$''. The metatheorem
    is applicable to this statement and thus a stalk is zero if and only if~$\F$
    is zero on a neighbourhood.
  \end{block}

  \vspace{1cm}
  \begin{alertblock}{Dictionary of external vs. internal notions}
    Expository notes are available at \url{http://tiny.cc/topos} (work in
    progress).
  \end{alertblock}
  \tiny\rmfamily\justifying
  Contents:
  Tensor product of sheaves $=$ internal ordinary tensor product,
  quasicoherent sheaves $=$ internal ordinary modules satisfying an interesting
  condition,
  internal Cartier divisors,
  more metatheorems about spreading of properties,
  pullback along immersions $=$ internal sheafification,
  relative spectrum $=$ internal spectrum,
  scheme dimension $=$ internal Krull dimension of~$\O_X$,
  dense $=$ not not,
  modal operators,
  other toposes,
  group schemes $=$ groups,
  \ldots
\end{column}

@@
